Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-03-08 pldi14/sec-change-structures.tex
Fix footnote placement

\pg{Recheck, verify or drop.}
Instead of representing a \emph{family} of change sets $\Delta v$ indexed by
$v \in V$ directly, one can just have a single set of all changes, and use
$\Term{src}$ to map a change $d_v \in \Delta V$ to its base value $v$ belonging
to the index set $V$. I believe that $\Term{src}$ is technically a
fibration\footnote{\url{http://ncatlab.org/nlab/show/fibration\#fibrations_in_category_theory}},
but I am not familiar with the theory of fibration enough to be sure.

>>>>

\pg{Recheck, verify or drop.}
Instead of representing a \emph{family} of change sets $\Delta v$ indexed by
$v \in V$ directly, one can just have a single set of all changes, and use
$\Term{src}$ to map a change $d_v \in \Delta V$ to its base value $v$ belonging
to the index set $V$. I believe that $\Term{src}$ is technically a
fibration,\footnote{\url{http://ncatlab.org/nlab/show/fibration\#fibrations_in_category_theory}}
but I am not familiar with the theory of fibration enough to be sure.
